---
title: "P8105_hw5_REN XIN"
output: github_document
date: "2022-11-16"
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(purrr)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


##Problem 1
Solution from Jeff
```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

##Problem 2

1.Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
Homicide = read_csv("data/homicide-data.csv") 
```

There are total 52,179 entries and 12 columns in Homicide database. Variables include `uid`, `reported_date`, `victim_last`, `victim_first`, `victim_race`, `victim_age`, `victim_sex`, `city`, `state`, `lat`,`lon`, and `disposition`. 

- Cleaning the data

```{r}
Homicide_df = Homicide %>% 
  janitor::clean_names() %>% 
   mutate(
    victim_sex = as.factor(victim_sex),
    state = as.factor(state)
  ) %>% 
  unite('city_state',"city":"state", remove = FALSE)%>%
  mutate(
    city_state = 
      str_c(city, ", ", state),
    solved_or_not = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  )%>% 
  select(-city, -state, -disposition) %>% 
  filter (city_state != "Tulsa_AL")
```
When processing the data we found an error in the name of the city and state of Tulsa, so I removed this data.



```{r}
Homicide_df_cities = Homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(solved_or_not == "unsolved"),
    percent_unsolved = round(unsolved_homicides*100 / total_homicides, 1)
  ) %>% 
  arrange(desc(total_homicides))
Homicide_df_cities = Homicide_df_cities[!rownames(Homicide_df_cities) %in% c("51") , ]

```






